Detecting the impact of land cover change on observed rainfall.

### 2019-07-29 Manuscripts/PeerJRainfall_Landuse/Rainfall_Landuse.Rmd
small changes before production

The pixels, where the tree cover change based on the MOD44B data was significant ($p \leq 0.05$) in each study region, are shown in Figure \@ref(fig:tctrend) for the NSW/VIC region  (left panel) and the QLD region (right panel). In the QLD region there actually has generally been an increase in tree cover after the clearing of native vegetation stopped. In the NSW/VIC region, much of the tree loss between 2002 and 2003 was concentrated in the Snowy Mountains close to the border of NSW and VIC, which is also evident in the figure. Tree cover loss occurred in large parts of the QLD region between 2002 and 2005, but this tree loss was spatially less concentrated.

>>>>

The pixels, where the tree cover change based on the MOD44B data was significant ($p \leq 0.05$) in each study region, are shown in Figure \@ref(fig:tctrend) for the NSW/VIC region  (A) and the QLD region (B). In the QLD region there actually has generally been an increase in tree cover after the clearing of native vegetation stopped. In the NSW/VIC region, much of the tree loss between 2002 and 2003 was concentrated in the Snowy Mountains close to the border of NSW and VIC, which is also evident in the figure. Tree cover loss occurred in large parts of the QLD region between 2002 and 2005, but this tree loss was spatially less concentrated.

### 2019-07-29 Manuscripts/PeerJRainfall_Landuse/SupplementaryMaterialRainfall_Landuse.Rmd
small changes before production

---
title: Detecting the impact of land cover change on observed rainfall.
preprint: false
author:
  - name: Chun X. Liang
    affiliation: 1
  - name: Floris F. van Ogtrop
    affiliation: 1
  - name: R. Willem Vervoort
    affiliation: 1
    corresponding: true
    email: willem.vervoort@sydney.edu.au
affiliation:
  - code: 1
    address: Sydney Institute of Agriculture, The University of Sydney, NSW 2006
abstract: >
  This is the supplementary data for the paper "Detecting the impact of land cover change on observed rainfall." Peerj article number 35847 
header-includes: >
 \usepackage{lipsum}
 \usepackage{textcomp, rotating}
 \usepackage[normalem]{ulem}
bibliography: reflist_chap3.bib
date: "`r Sys.Date()`"
output:
  bookdown::pdf_book:
    base_format: rticles::peerj_article # for using bookdown features like \@ref()
  rticles::peerj_article: default
---
```{r setup, warning=F, message=F, echo =F}
# root dir
knitr::opts_knit$set(root.dir =
      # "E:/cloudstor/chun/chun/manuscripts/PeerJRainfall_Landuse")
      "C:/users/rver4657/owncloud/chun/chun/manuscripts/PeerJRainfall_Landuse")
knitr::opts_knit$set('figcap.prefix','Figure S')
knitr::opts_knit$set('tabcap.prefix','Table S')
```

>>>>

---
title: Detecting the impact of land cover change on observed rainfall.
preprint: false
author:
  - name: Chun X. Liang
    affiliation: 1
  - name: Floris F. van Ogtrop
    affiliation: 1
  - name: R. Willem Vervoort
    affiliation: 1
    corresponding: true
    email: willem.vervoort@sydney.edu.au
affiliation:
  - code: 1
    address: Sydney Institute of Agriculture, The University of Sydney, NSW 2006
abstract: >
  This is the supplementary data for the paper "Detecting the impact of land cover change on observed rainfall." Peerj article number 35847 
header-includes: >
 \usepackage{lipsum}
 \usepackage{textcomp, rotating}
 \usepackage[normalem]{ulem}
bibliography: reflist_chap3.bib
date: "`r Sys.Date()`"
output:
  bookdown::pdf_book:
    base_format: rticles::peerj_article # for using bookdown features like \@ref()
  rticles::peerj_article: default
---
\renewcommand{\figurename}{Figure S}
```{r setup, warning=F, message=F, echo =F}
# root dir
knitr::opts_knit$set(root.dir =
      # "E:/cloudstor/chun/chun/manuscripts/PeerJRainfall_Landuse")
      "C:/users/rver4657/owncloud/chun/chun/manuscripts/PeerJRainfall_Landuse")
```
